GMSE: an R package for generalised management strategy evaluation

### 2017-10-18 notebook/ms/ms.Rmd
Better parameter simulations, now that GMSE has been updated

```{r, echo = TRUE}
sim <- gmse(land_ownership = TRUE, stakeholders = 10, observe_type = 0, 
            res_death_K = 2000, manage_target = 1000, RESOURCE_ini = 1000, 
            user_budget = 5000, manager_budget = 5000, res_consume = 1, 
            scaring = TRUE, times_observe = 1, plotting = FALSE);
```

>>>>

```{r, echo = TRUE}
sim <- gmse(land_ownership = TRUE, stakeholders = 5, observe_type = 0, 
            res_death_K = 2000, manage_target = 1000, RESOURCE_ini = 1000, 
            user_budget = 1000, manager_budget = 1000, res_consume = 1, 
            scaring = TRUE, plotting = FALSE);
```
